---
title: Inherited instructions
author: Pierce Edmiston
bibliography: references.bib
csl: apa.csl
output:
  beamer_presentation:
    theme: metropolis
    includes:
      in_header: header.tex
---
```{r config, include=FALSE}
library(knitr)
library(crotchet)
library(gridExtra)
opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, cache = TRUE)
sapply(list.files("R", "*.R", full.names = TRUE), read_chunk)
```
```{r theme, include=FALSE, cache=FALSE}
library(ggplot2)
theme_set(theme_minimal(base_size=16))
```

# Totems

```{r totems, include=FALSE}
```

```{r totems-game}
draw_image("derex-boyd-2015-fig2", package = "totems")
```

# Totems: Landscape

```{r totems-landscape-and-recipes}
grid.arrange(
  read_image("landscape-sample.gv", package = "totems"),
  read_image("recipes.gv", package = "totems"),
  nrow = 1,
  widths = c(0.6, 0.4)
)
```

# Totems: Tools

```{r totems-landscape-tools, out.height="85%"}
draw_image("landscape-tools.gv", package = "totems")
```

# Totems: Explanations

> Make sure that you use the rock as much as possible because it yields the most results. Strategies that worked was when creating a new tool, test that new tool with every other tool or resource because that often created something new. In the end I spent a lot of time trying to create a stump because that is how you build the totem so use the tools and work with the different trees to try and build the stumps. The most confusing part was initially starting and trying to decide what to test first so don’t hesitate, just simply go for it.

# Totems: Explanations

> I would tell them to think carefully about the materials and re-read the directions. I would tell them to try different combinations with the sturdy materials and try to make new things out of the trees as well. I found that guessing with the berries did not work and filling out all four spaces also did not work. I found it difficult/ confusing on how to actually build the pole and what to do once I ended up with certain resources.

# Totems: Explanations

> To begin with, use your rocks. Rocks with rocks, rocks with those advanced rocks, advanced rocks with more advanced items and you’ll get a lot of combinations. The berries, not much help. Use your rocks the most. It helps if you make doubles of items and then try combining those to make more new items. Find a pattern and stick to it.

# Totems: Explanations

> \scriptsize The last item I discovered was the string, I am guessing that some combination of the string with either the wood poles or the block of larger wood will give you a block. A combination of the string with one of the types of arrowhead may give you a new tool but I doubt it as I think I tried most of them. Also I think the berries are used much later in the game as an item you can use to dye the blocks of wood to make more points from the totem pole. One last piece of advice would be to try multiple of a material to see if something is produced. An example would be to try two or three arrowheads together by them self and then adding another material or tool. When you go through a cold patch where you are not making any progress take stop clicking, take your hand off the mouse and take a deep breath. Then try to think of what real life combinations would yield objects you could use.

# Totems: Explanations

> Use common sense to think of combinations, but also throw things together you might not think work. I didn’t expect some of the stuff to work and it did.

# Totems: Explanations

> You got to keep making combos until something works. Make them big because I tried all the all the 1 by 1’s. The game is a spoof, so don’t get mad or frustrated. Try and do like 3 different items in the box because I couldn’t get through all those combos.

# Totems: Number of innovations

```{r totems-num-innovations}
num_innovations_plot
```

# Totems: Rate of innovation

```{r totems-rate-of-innovation}
rate_of_innovation_plot
```

# Totems: Summary

- Participants were able to generate useful instructions.
- Instructions were useful in different ways that are hard to quantify.
- No clear benefit to inheriting instructions **over and above** inheriting tools.

# Gems

```{r gems, include=FALSE}
```

```{r gems-solution-space}
gridExtra::grid.arrange(
  read_image("SimpleHillGems", package = "gems"),
  simple_hill_landscape,
  nrow = 1,
  widths = c(0.4, 0.6)
)
```

# Gems: Procedure

```{r gems-procedure}
grid.arrange(
  read_image("inherited-instructions-trial", package = "gems"),
  trial_plot,
  nrow = 1
)
```

# Gems: Overall performance

```{r gems-overall}
score_by_block_plot
```

# Gems: Instructions

```{r gems-instructions-coded}
grid.arrange(
  instructions_coded_plot,
  instructions_summarized_plot,
  nrow = 1
)
```

# Gems: Instructions - Nothing Useful

> I believe that the more precious gems are on the left side. I believe the left most gem has a slight variablity. It ranges from plus 3 to negative 3, and The ones closer to the middle have greater ranges. The ones on the furthest to the left have the greatest ranges.

\vspace{1em}

> Stick with the same few gems and keep clicking them I think it is better to do that then go completely random.

# Gems: Instructions - 2D correct

> The gems went up in value when the lines became more horizontal.  Also, the amount of lines matters. More lines is good, but don't let the lines get too small where the top and bottom of the gem are no longer black otherwise the gems go down in value. Also, more defined lines on the gems usually make them more valuable.

\vspace{1em}

> I think the gems tilted at 10 degrees are most valuable. I also think that the gems with the biggest lines out of the 5 on the screen are the least valuable. Do not click the same gem more than 3 times in a row.

# Gems: Instructions - 1D correct

\scriptsize

> It took me a while to find a pattern, but what I found is that a gem becomes more valuable when it is rotated clockwise. To clairfy, when the bars more and more to the right. Howeve, I found that when it got to the center, it went the other way, so counterclockwise.

\vspace{1em}

> The valued gems have thin stipes on them, but once the stripes are too thin the value decreases. The direction of stripes does not matter.

# Gems: Instructions - Mention 2D

> The gems that are most valuable are the ones with the most stripes and are slanted the most. Pay attention to the tops of the gems.

# Gems: Instructions - ?

> the lines form about 45 degree with the horizontal line. Should not be too dense. Black and white lines should be about the same width. 

\vspace{1em}

> I believe that the gems alternate from left to right and you have to select a certain gem based on the thickness of the lines located within it. I feel like if you had a thick one it would be the thinner one and than if you had a thin on it would become a thicker one.

# Gems: Instructions outcomes

```{r gems-instructions-outcomes}
grid.arrange(
  instruction_quality_and_performance_plot,
  instruction_quality_and_final_performance_plot,
  nrow = 1,
  widths = c(0.6, 0.4)
)
```

# Gems: Gen2 versus Gen1

```{r gems-block1-by-instructions-type}
instructions_versus_no_instructions_plot
```

# Gems: Gen2 - Gen1

```{r gems-diff}
diff_plot
```

# Gems: Gen2 - Gen1

```{r gems-overall-diff}
overall_diff_plot
```

# Gems: Canalization

```{r gems-canalization}
grid.arrange(
  canalization_bar_width_plot + ggtitle("Bar width") + theme(legend.position = c(0.8, 0.2)),
  canalization_orientation_plot + ggtitle("Orientation") + theme(legend.position = "none"),
  nrow = 1
)
```

# Rockets

```{r rockets, include=FALSE}
```

```{r rockets-categories, out.height="80%"}
draw_image("rocket-categories", package = "rockets")
```

# Rockets: Performance

```{r rockets-performance}
accuracy_plot
```

# Rockets: Descriptions

> A rockets have longer wings B rockets have shorter wings

\vspace{1em}

> Smaller triangles are B unless it also has a large circle/oval

\vspace{1em}

> Type A rockets tend to be shorter and sleeker, while Type B rockets tend to be bulkier.

\vspace{1em}

> Type A rockets are generally more balanced in appearance. Type B have unequal proportions.

# Rockets: A hero!

\scriptsize

> Check the circles between both rockets. Also see the base.

\vspace{1em}

> Check the ovals and the base Type A has both with a small circle and base or a large circle and base. Type B has a mix of small circle or base with a large circle or base

```{r rockets-correct, out.height="60%"}
accuracy_plot %+% filter(Rockets, workerId == "AHKRGPN5D3I2G")
```

# Person who inherited?

\scriptsize

> The type A has a circle that is similar to B, but it’s different. You can also clearly tell the difference in the fins.

\vspace{1em}

> The A is distinct from the B in the design of the wings and rocket nozzle.

```{r rockets-inherited, out.height="60%"}
accuracy_plot %+% filter(Rockets, workerId %in% c("A25R2OI9L2Q1OW", "AHKRGPN5D3I2G"))
```
